---
title: "titanic_clean"
author: "Drew Hall"
date: "July 7, 2018"
output: html_document
---

```{r}
library(dplyr)
library(tidyr)

library(readxl)
Copy_of_titanic3_csv <- read_excel("C:/Users/Pinea/OneDrive/Copy of titanic3.csv.xls")
View(Copy_of_titanic3_csv)
```

```{r}
titanic1 <- Copy_of_titanic3_csv
```
There were a lot of missing values in the embarked column that were later found to be people from SouthHampton, which is signified with an S. So I replaced the na's with an S!

```{r}
titanic1 <- titanic1 %>% replace_na(list(embarked = "S"), embarked)
```
There were alot of ages missing as well. So, I went ahead and used a mean of all the ages to fill in the ages so it could be plotted better. 
```{r}
M <- mean(titanic1$age, na.rm = TRUE)
titanic1<-titanic1 %>% replace_na(list(age = M), age)

```
Created a dummy variable for all of the empty boats. 
```{r}
titanic1 <- titanic1 %>% replace_na(list(boat = "None"), boat)
```
Creating a binary dummy code was needed to help gain insight on who had a room number. This was useful to see who made it off of the boat and who did not. 
```{r}
titanic1 <- titanic1 %>% mutate(has_cabin_number = ifelse(is.na(cabin), 0,1))
```

```{r}
View(titanic1)
```

